Methodology for Assessing the State of the Practice for Domain X

### 2020-11-10 StateOfPractice/Methodology/Methodology.tex
Revisions to Research Questions section

The following are research questions that we want to answer to assess the state
of practice of research software in our chosen domain:

\begin{enumerate}
\item What are the artifacts that current software packages consist of? 
\item What tools are used by current software packages?
\item What principles, processes, and methodologies are used in the development
  of current software packages?
\item What are the pain points for developers working on SCS projects? What
  aspects of the existing processes, methodologies and tools do they consider
  could potentially be improved? What processes, methodologies and tools have
  they changed to reduce obstacles?
\item For research software developers, what specific actions are taken to address the following:
\begin{enumerate}
\item usability \pmi{question to developers 11}
\item traceability \pmi{question to developers 3}
\item modifiability \pmi{question to developers 9}
\item maintainability \pmi{question to developers 9}
\item correctness \pmi{question to developers 8}
\item understandability \pmi{question to developers 10}
\item unambiguity \pmi{question to developers 12}
\item reproducibility \pmi{question to developers 13}
\item visibility/transparency \pmi{question to developers 3}
\end{enumerate} 
\item How does software designated as high quality by this methodology compare
  with top rated software by the community?
\end{enumerate}

>>>>

The following are the research questions that we wish to answer for each of our
selected domains.  In addition to answering the questions for each domain, we
also wish to combine the data from multiple domains to answer these questions
for research software in general.

\begin{enumerate}
\item What artifacts are present in current software packages? 
\item What tools are used by current software packages?
\item What principles, processes, and methodologies are used in the development
  of current software packages?
\item What are the pain points for developers working on research software
  projects?  What aspects of the existing processes, methodologies and tools do
  they consider as potentially needing improvement?  How should processes,
  methodologies and tools be changed to improve software development and
  software quality?
\item For research software developers, what specific actions are taken to
  address the following:
\begin{enumerate}
\item usability \pmi{question to developers 11}
\item traceability \pmi{question to developers 3}
\item modifiability \pmi{question to developers 9}
\item maintainability \pmi{question to developers 9}
\item correctness \pmi{question to developers 8}
\item understandability \pmi{question to developers 10}
\item unambiguity \pmi{question to developers 12}
\item reproducibility \pmi{question to developers 13}
\item visibility/transparency \pmi{question to developers 3}
\end{enumerate} 
\item How does software designated as high quality by this methodology compare
  with top rated software by the community?
\end{enumerate}
